### 2018-08-10 Sections/protocols_for_the_quantum_internet.tex
minor

\comment{Get Tim to expand on this with ideas that were discussed in Shanghai.}

Clock synchronisation is a fundamental task with widespread applications, ranging from navigation, telecommunications, financial transactions, the internet, and many scientific applications. Of these, the Global positioning system (GPS)\index{Global positioning system (GPS)} has become a day-to-day necessity for much of humanity, having been increasingly incorporated into smartphones and other commodity devices.

The GPS system famously relies upon very precise clock synchronisation to perform its task through a process of quadrangulation\index{Quadrangulation} from a constellation of several satellites. Due to the high speed of light, one requires in practice highly synchronised clocks which are accurate to a centralised time standard to the nanosecond level. This allows positioning to be performed to the level of meters, which is acceptable for many routine applications. GPS satellites have atomic clocks that are stable to one part in $10^{13}$, so that active correction can maintain accuracy to the nanosecond level. The great success of the GPS system in turn has created a further demand for increasingly precise navigation. For example, autonomous vehicles would immediately benefit from a more precise navigation system.

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ClockSync($\frac{1}{\sqrt{2}}(\ket{0}\ket{1} - \ket{1}\ket{0})$):
\begin{enumerate}
\item Distribute a Bell state between Alice and Bob,
\begin{align}
\ket{\psi_0} &= \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B - \ket{1}_A\ket{0}_B)\nonumber\\
	&= \frac{1}{\sqrt{2}}(\ket{+}_A\ket{-}_B - \ket{-}_A\ket{+}_B).
\end{align}
\item The joint system is assumed to be freely-evolving under the Hamiltonian,
\begin{align}
\hat{H} = \hbar\omega(\hat{Z}_A + \hat{Z}_B).	
\end{align}
\item Over time $t_\mathrm{free}$ this evolves the initial state to,
\begin{align}
	\ket{\psi_1} &= e^{-i\hat{H} t_\mathrm{free}}\frac{1}{\sqrt{2}}(\ket{+}_A\ket{-}_B - \ket{-}_A\ket{+}_B)\nonumber\\
	&= e^{-i\omega t_\mathrm{free}}\frac{1}{\sqrt{2}}(\ket{+}_A\ket{-}_B - \ket{-}_A\ket{+}_B),
\end{align}
yielding only an irrelevant global phase.
\item Alice measures her qubit in the $\hat{X}$ basis ($\ket\pm\bra\pm$), and classically announces the time at which she performed the measurement, $t_A$, and her measurement outcome, \mbox{$m_A=\pm$}.
\item The system evolves for time $t_\mathrm{ev}$,
\begin{align}
	\ket{\psi_{+}} &= e^{-i\hat{Z} t_\mathrm{ev}}\ket{-}_B\nonumber\\
	&\propto \ket{0}_B-e^{-i\omega t_\mathrm{ev}}\ket{1}_B,\nonumber\\
	\ket{\psi_{-}} &= e^{-i\hat{Z} t_\mathrm{ev}}\ket{+}_B\nonumber\\
	&\propto \ket{0}_B+e^{-i\omega t_\mathrm{ev}}\ket{1}_B.
\end{align}
\item Bob measures his qubit in the $\hat{X}$ basis, with measurement probabilities,
\begin{align}
	m_+ &\propto \sin^2(\omega t_\mathrm{ev}),\nonumber\\
	m_- &\propto \cos^2(\omega t_\mathrm{ev}).
\end{align}
\item Bob sets his clock to,
\begin{align}
	t_B = t_A+t_\mathrm{ev}.
\end{align}
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Algorithm for performing quantum clock synchronisation between two parties using shared Bell-pairs and classical communication.\comment{Check this for errors!}} \label{alg:clock_sync}
\end{table}

>>>>

Clock synchronisation is a fundamental task with widespread applications, ranging from navigation, telecommunications, and financial transactions, to the internet as a whole, and many scientific applications. Of these, the global positioning system (GPS)\index{Global positioning system (GPS)} has become a day-to-day necessity for much of humanity, having been increasingly incorporated into smartphones and other commodity devices.

The GPS system famously relies upon very precise clock synchronisation to perform its task through a process of quadrangulation\index{Quadrangulation} from a constellation of several satellites\index{Constellation network}. Due to the high speed of light, we require highly synchronised clocks, accurate to the nanosecond level. This allows positioning to be performed to the level of meters, a level of precision required for many routine applications. GPS satellites have atomic clocks that are stable to one part in $10^{13}$, so that active correction can maintain this level of accuracy.

The great success of the GPS system has created a further demand for increasingly precise navigation. For example, autonomous vehicles would immediately benefit from a more precise navigation system.

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ClockSync($\frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B - \ket{1}_A\ket{0}_B)$):
\begin{enumerate}
\item Distribute a Bell state between Alice and Bob,
\begin{align}
\ket{\psi_0} &= \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B - \ket{1}_A\ket{0}_B)\nonumber\\
	&= \frac{1}{\sqrt{2}}(\ket{+}_A\ket{-}_B - \ket{-}_A\ket{+}_B).
\end{align}
\item The joint system is freely-evolving under the Hamiltonian,
\begin{align}
\hat{H} = \hbar\omega(\hat{Z}_A + \hat{Z}_B).	
\end{align}
\item Over time $t_\mathrm{free}$ this evolves to,
\begin{align}
	\ket{\psi_1} &= e^{-i\frac{\hat{H}}{\hbar} t_\mathrm{free}}\frac{1}{\sqrt{2}}(\ket{+}_A\ket{-}_B - \ket{-}_A\ket{+}_B)\nonumber\\
	&= e^{-i\omega t_\mathrm{free}}\frac{1}{\sqrt{2}}(\ket{+}_A\ket{-}_B - \ket{-}_A\ket{+}_B),
\end{align}
yielding only an irrelevant global phase.
\item Alice measures her qubit in the $\hat{X}$ basis ($\ket\pm\bra\pm$), and classically announces the time at which she performed the measurement, $t_A$, and her measurement outcome, \mbox{$m_A=\pm$}.
\item The system evolves for time $t_\mathrm{ev}$,
\begin{align}
	\ket{\psi_{+}} &= e^{-i\hat{Z} t_\mathrm{ev}}\ket{-}_B\nonumber\\
	&\propto \ket{0}_B-e^{-i\omega t_\mathrm{ev}}\ket{1}_B,\nonumber\\
	\ket{\psi_{-}} &= e^{-i\hat{Z} t_\mathrm{ev}}\ket{+}_B\nonumber\\
	&\propto \ket{0}_B+e^{-i\omega t_\mathrm{ev}}\ket{1}_B.
\end{align}
\item Bob measures his qubit in the $\hat{X}$ basis, with measurement probabilities,
\begin{align}
	m_+ &\propto \sin^2(\omega t_\mathrm{ev}),\nonumber\\
	m_- &\propto \cos^2(\omega t_\mathrm{ev}),
\end{align}
and infers $t_\mathrm{ev}$.
\item Bob sets his clock to,
\begin{align}
	t_B = t_A+t_\mathrm{ev}.
\end{align}
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Algorithm for performing quantum clock synchronisation between two parties using shared Bell-pairs and classical communication.\comment{Check this for errors!}} \label{alg:clock_sync}
\end{table}
